\chapter{War, Disease, Sanitation}

\begin{RefWord}{sanitation}
    the protection of public health by removing and treating waste, dirty water etc
    \textit{Overcrowding and poor sanitation are common problems in prisons. 过度拥挤和卫生状况差是监狱里的普遍问题。}
\end{RefWord}

\section{turb （to stir)}

\begin{DefWord}{disturb, disturbing, disturbance, disturbed}[disturb]
    to interrupt someone so that they cannot continue what they are doing
    \textit{\textbf{Sorry to disturb you}, but I have an urgent message.对不起，打扰一下，我有个紧急消息。}

    to make someone feel worried or upset
    \textit{What disturbs you most about this latest development?}

    to move something or change its position
    \textit{If you find a bird's nest, never disturb the eggs.}

    to change a normal situation in a way that causes problems
    \textit{New procedures often disturb the comfortable habits of the workforce.}
    \textit{My hormone balance is disturbed by my pregnancy.}


    \textbf{disturb somebody's sleep}
    \textit{Local people said their sleep was being disturbed by the noise from the aircraft.}

    \textbf{disturb somebody's concentration}
    \textit{I couldn't work with the kids around disturbing my concentration.}

    disturbance: a situation in which people behave violently in public 骚乱，骚动
    \textit{There were disturbances in the crowd as fans left the stadium.}

    \textbf{create/cause a disturbance}
    \textit{army training on controlling \textbf{civil disturbance}}

    something that interrupts what you are doing, or the act of making this happen
    \textbf{disturbance to}
    \textit{When a helicopter lands, it can \textbf{cause a disturbance to} local residents.}

    a medical condition in which someone is mentally ill and does not behave normally 精神障碍
    a history of mental disturbance


\end{DefWord}

\begin{DefWord}{turmoil}
    a state of confusion, excitement, or anxiety

    \textbf{political/emotional/economic/religious etc turmoil}
    \textit{the prospect of another week of political turmoil}

\end{DefWord}

\begin{DefWord}{turbid, turbidity}
    \textbf{turbid water} or liquid is dirty and muddy


\end{DefWord}

\begin{DefWord}{perturbed, perturb}[perturbed]
    worried about something that has happened or will happen

    \textbf{perturbed by/at/about}
    \textit{ He didn't seem perturbed by the noises outside.}

    perturb: \textit{My unexpected arrival didn't perturb him in the least.}
\end{DefWord}

\begin{DefWord}{turbulent, turbulence}[turbulent]
    a turbulent situation or period of time is one in which there are a lot of sudden changes
    \textit{the turbulent times of the French Revolution}

    \textbf{turbulent air or water} moves around a lot
    \textit{ the dark turbulent waters of the river}
\end{DefWord}

\section{bell (to fight)}

\begin{DefWord}{rebel, rebellious, rebellion}[rebel]
    noun /ˈrebəl/, verb /rɪˈbel/
    someone who opposes or fights against people in authority

    \textbf{rebel forces/soldiers/leader}

    someone who refuses to do things in the normal way, or in the way that other people want them to
    \textit{Alex has always been a bit of a rebel.亚历克斯向来有点叛逆。}

    to oppose or fight against someone in authority or against an idea or situation which you do not agree with
    \textbf{rebel against}
    \textit{teenage boys rebelling against their parents}

    if your stomach, legs, mind etc rebel, you cannot do or believe something you think you should〔胃、腿、头脑等〕不听使唤:
    \textit{He knew he ought to eat, but his stomach rebelled.}

    rebellion: an organized attempt to change the government or leader of a country, using violence 造反；叛乱；起义 ($\rightarrow$ coup, revolution)

    when someone opposes or fights against people in authority or ideas which they do not agree with
    \textit{a rebellion by right-wing members of the party}
    \textit{\textbf{rebellion against} traditional values}

    rebellious: deliberately not obeying people in authority or rules of behaviour 叛逆的；反叛的；反抗的
    \textit{rebellious teenagers}
    \textit{He's always had a rebellious streak (=a tendency to rebel).他向来个性叛逆}
\end{DefWord}

\begin{DefWord}{belligerent, belligerence, belligerency}[belligerent]
    very unfriendly and wanting to argue or fight
    \textit{a belligerent attitude}

    \textbf{a belligerent country} is fighting a war against another country

    belligerency: (国与国等处于)交战中；好战性

    \textit{Whether it works or not, it shows how much the nature of modern belligerency is changing.}
    
    belligerence: 好战性；交战

    \textit{His reputation for savagery and belligerence is nothing but a myth.}
\end{DefWord}

\begin{DefWord}{bellicose, bellicosity}[bellicose]
    behaving in a way that is likely to start an argument or fight
    (aggressive)
    \textit{bellicose criticism}

\end{DefWord}

\begin{DefWord}{bellow}
    to shout loudly in a deep voice 
    \textit{'That's your problem!' bellowed Hurley.}

    a loud deep shout

    bellows [plural]: 风箱
\begin{itemize}
    \item an object used for blowing air into a fire to make it burn better
    \item part of a musical instrument that pushes air through pipes to produce a sound, for example in an organ
\end{itemize}

\end{DefWord}


\section{bat (to beat/to strike)}

\begin{DefWord}{combat, combatant, combative}[combat]
    fighting, especially during a war
    \textit{training in \textbf{unarmed combat} (=fighting without weapons) 徒手格斗训练}
    \textit{We flew over 200 \textbf{combat missions}.}

    a fight or battle

    combats [plural]: loose trousers, often with many pockets

    \textbf{hand-to-hand combat}
    \textit{Thousands of men were killed in hand-to-hand combat in less than 24 hours.}

    \textbf{close combat}
    \textit{Swords and spears were used for close combat.}

    \textbf{single combat}
    \textit{The champion called out a challenge to single combat.}

    \textbf{mortal combat 殊死的战斗}
    \textit{an exciting computer game of mortal combat against giants and monsters}

    \textbf{air/aerial combat}
    (=fighting in the air)
\textit{30 enemy aircraft were destroyed in aerial combat.}

\textbf{be locked in combat}
(=to be using all your effort and attention to fight each other)
\textit{Their troops were locked in combat.}

\textbf{engage in combat with somebody}
formal (=to fight someone)
\textit{The president said he was aware of the danger to forces engaged in combat in the field.}

\textbf{combat + NOUN}
\textbf{combat troops/soldiers/forces/units}
\textit{US combat troops were in the streets of the capital yesterday.}

\textbf{combat aircraft}
\textit{Very few combat aircraft have been destroyed.}

\textbf{combat vehicles}
\textit{Armoured combat vehicles appeared on the streets of the city.}

\textbf{a combat zone}
(=an area where there is fighting)
\textit{refugees from the combat zone}

\textbf{a combat mission/operation}
\textit{He flew 280 combat missions in two wars.}

\textbf{combat gear}
(=clothes worn in battles by the armed forces)
\textit{a group of soldiers in combat gear}

\textbf{combat fatigues}
(=trousers worn in battles by the armed forces)
\textit{He was still dressed in combat fatigues and jungle boots.}

\textbf{combat boots}
\textit{The troops were issued with steel helmets and combat boots.}

\textbf{combat readiness}
(=the state of being ready to fight)
\textit{Troops had been flown in and were in combat readiness.}

combative: ready and willing to fight or argue 好斗的；好争论的:
\textit{ Congress is in a combative mood. 国会斗志昂扬。}

\end{DefWord}

\begin{DefWord}{debate}
\textit{The new drug has become the subject of \textbf{heated debate} within the medical profession.}

\textit{There has been widespread \textbf{public debate} \textbf{over} the introduction of genetically modified food.}

\textit{There was much \textbf{lively debate} about whether women should spend more time in the home.}

\textit{A fierce \textbf{debate raged over} which artist's work should be chosen for the prize. 就哪位艺术家的作品应该得奖一事展开了激烈的争论。}

\textit{the \textbf{ongoing debate} between environmentalists and the road-building lobby over the future of our countryside}

\textit{Nuclear power has always been a topic that has sparked off considerable debate. 核电一直是引起相当多争议的话题。}



\end{DefWord}


\begin{DefWord}{battle}
\end{DefWord}

\begin{DefWord}{batter}
    to hit someone or something many times, in a way that hurts or damages them
    \textit{He was \textbf{battered to death.}}

    \textbf{batter at/on/against etc}
    \textit{People were battering at the door.}

    \textbf{batter somebody with something}
    \textit{He was battered on the head with a cricket bat.}

    \textbf{batter away}
    \textit{She battered away at his chest with her fists.}

    \textbf{batter something down}
    \textit{Armed police battered his door down.}

    mixture of flour, eggs, milk etc, used in cooking and for making bread, cakes etc 〔面粉、鸡蛋、牛奶等调成的〕面糊:
    \textit{Fry the fish in batter. 把鱼蘸上面糊油炸。}

    the person who is trying to hit the ball in baseball 〔棒球〕击球手
\end{DefWord}


\begin{DefWord}{rebate}
    an amount of money that is paid back to you when you have paid too much tax, rent etc 〔税、租金等的〕退款:
 \textit{You may be entitled to a tax rebate. 你也许可以享受退税。}
\end{DefWord}

\begin{DefWord}{abate}
    to become less strong or decrease (subside)

    \textit{We waited for the storm to abate.}
\end{DefWord}

\section{term/termin (to limit)}

\begin{DefWord}{terminate, termination, terminator}[terminate]
    if something terminates, or if you terminate it, it ends
    \textit{a woman's decision on whether or not to \textbf{terminate the pregnancy}}

    if a train, bus, or ship terminates at a particular place, its journey ends there
    \textit{The train from Paris terminates at St Pancras International.}

    termination:
    \textit{You may face a reduction or \textbf{termination of} benefits.}

    a medical operation to end the life of a developing child before it is born (abortion)
\end{DefWord}

\begin{DefWord}{terminal, terminally}[terminal]
    \textit{the airport's passenger terminal}

    one of the points at which you can connect wires in an electrical circuit〔电路的〕端子
\textbf{positive/negative terminal}

a piece of computer equipment consisting of at least a keyboard and a screen, that you use for putting in or taking out information from a large computer

\textbf{a terminal illness} cannot be cured, and causes death (fatal)

\textbf{(in) terminal decline} in a state of becoming worse and worse and never getting better 越来越糟；奄奄一息:
 \textit{The once great industry is now in terminal decline.}

 \textit{terminally ill patients}
\end{DefWord}

\begin{DefWord}{determine, determined, determinant, determination}[determine]
    determinant (noun):  something that strongly influences what you do or how you behave
    \textit{Social class is a major determinant of consumer spending patterns.}

    determined: having a strong desire to do something, so that you will not let anyone stop you
    \textit{Gwen is a very determined woman.}
    \textit{She was \textbf{determined to} win.}
    \textit{He was \textbf{determined that} the same mistakes would not be repeated.}

    showing determination, especially in a difficult situation
    \textit{She was making a determined effort to give up smoking.}
    \textit{The library was closed down despite \textbf{determined opposition.}}

    determination: the quality of trying to do something even when it is difficult
    \textit{Yuri shows \textbf{great determination to} learn English.}
    \textit{his \textbf{dogged determination} (=very strong determination) to succeed}

    the act of deciding something officially
    \textit{the determination of government policy}

    the act of finding the exact level, amount, or cause of something
    \textit{accurate determination of the temperature}
\end{DefWord}

\begin{remark}
    \begin{RefWord}{discriminate, discriminant, discriminative}[discriminate]
\end{RefWord}
\end{remark}


\begin{DefWord}{interminable, interminably}[interminable]
    very long and boring (endless)
    \textit{interminable delays}
    \textit{an interminably long speech}
\end{DefWord}

\begin{DefWord}{exterminate, exterminator, extermination}[exterminate]
    to kill large numbers of people or animals of a particular type so that they no longer exist
    \textit{Staff use the poison to exterminate moles and rabbits.}


\end{DefWord}


\section{tact/tag/tang (to touch)}

\begin{DefWord}{intact}
    complete and not damaged
    \textit{Most of the house remains intact even after two hundred years.}

\end{DefWord}

\begin{DefWord}{tact, tactful, tactfully, tackless}[tact]
    (noun) the ability to be careful about what you say or do, so that you do not upset or embarrass other people

    \textit{With great tact, Clive persuaded her to apologize.}

    tactful: not likely to upset or embarrass other people (opp tactless)
    \textit{There was no tactful way of phrasing what he wanted to say.}
\end{DefWord}

\begin{DefWord}{tactics}
    a method that you use to achieve something
    \textit{a \textbf{tactic employed} to speed up the peace process}

    \textit{Republicans accuse Democrats of using \textbf{delaying tactics} (=something you do in order to give yourself more time) to prevent a final vote on the bill.}

    \textit{Shock tactics are being used in an attempt to stop drink drivers. 正在采取“震慑策略”来制止司机酒后驾车。}

    \textbf{strong-arm tactics} (=the use of force, violence, or threats)
    \textit{Others were furious at what they said were government strong-arm tactics over the vote.}

    \textbf{a diversionary tactic} (=an action which draws attention away from something)
    \textit{Before the attack, nearby areas were bombed as a diversionary tactic.}

    \textbf{underhand/unfair tactics} (=actions which are not fair or honest)
    \textit{I wouldn't stoop to such sneaky, underhand tactics.}

    \textbf{change/switch tactics}
    \textit{Manchester United switched tactics in the second half.}

    \textbf{resort to a tactic} (=use a tactic because there is no other way to do something)
    \textit{Students resort to these tactics when they see no other way to address the problem.}

    \textbf{a tactic works (=is successful)}
    Those tactics won't work with me anymore - I know you too well.

    \textbf{a change of tactics}
    \textit{They trailed 2-1 at half time, but a change of tactics brought a 3-2 win.}

    tactics [plural]: the science of arranging and moving military forces in a battle

\end{DefWord}

\begin{DefWord}{contact}
    communication with a person, organization, country etc
    \textit{There is very little \textbf{contact between} the two tribes.}
    \textit{We stay \textbf{in contact} by email.}

    when two people or things touch each other
    \textit{Children need \textbf{physical contact} with a caring adult.}
    \textit{The disease spreads by \textbf{sexual contact} between infected animals.}
    \textit{For a second, his hand was \textbf{in contact with} mine. 那一瞬间，他的手和我的手碰到了一起。}
    \textit{When water \textbf{comes into contact with} air, carbon dioxide is released.}
    \textit{The bomb exploded \textbf{on contact} (=at the moment it touched something).}

    when you meet someone or experience a particular kind of thing
    \textit{Everyone who \textbf{came into contact with} Di felt better for knowing her.}
    \textit{Pat's job \textbf{brings} her \textbf{into contact with} the problems people face when they retire.}

    a person you know who may be able to help or advise you
    \textit{He has a lot of contacts in the media.}
    \textit{business/personal contacts}

    contacts [plural] a situation in which you can communicate easily with a group, country etc 社会关系
    \textbf{contact with/between}
    \textit{We have good contacts with the local community.}

    \textbf{point of contact}
    a)a place you go to or a person you meet when you ask an organization for help
    \textit{Primary health care teams are the first point of contact for users of the service.}

    a way in which two different things are related
    \textit{finding a point of contact between theory and practice}

    an electrical part that completes a circuit when it touches another part 〔电路的〕触点

    a contact lens 隐形眼镜
\end{DefWord}

\begin{DefWord}{contagious, contagion}[contagious]
    a disease that is contagious can be passed from person to person by touch (infectious)

    a person who is contagious has a disease that can be passed to another person by touch (infectious)
    \textit{The patient is still highly contagious.}

    if a feeling, attitude, or action is contagious, other people are quickly affected by it and begin to have it or do it (infectious)
    \textit{his contagious enthusiasm}
\end{DefWord}

\begin{DefWord}{tangible, intangible}[tangible]
    that can be clearly seen to exist; clear enough or definite enough to be easily seen or noticed
    \textit{\textbf{tangible benefits/improvements/results}, etc. 实际的好处、改进、效果等 }
    \textit{We cannot accept his findings without \textbf{tangible evidence}. 没有确凿的证据，我们不能接受他的发现。}
    \textit{\textbf{tangible assets} (= a company's buildings, machinery, etc.) 有形资产}

    if something is tangible, you can touch or feel it
    \textit{The silence of the countryside was almost tangible. 乡村的寂静几乎能感觉得到。}
\end{DefWord}



\begin{DefWord}{tactile}
    relating to your sense of touch (Somatosensation):
    \textit{tactile sensations}
    
    \textbf{a tactile person} likes to touch people, for example when talking to them

\end{DefWord}


\section{punct, pung, point (point/to sharpen)}

\begin{DefWord}{appoint, appointee, self-appoint, well-appointed}[appoint]
    to choose someone for a position or a job
    \textit{He's \textbf{been appointed to }the State Supreme Court. 他奉命到州最高法院任职。}
    \textit{A committee \textbf{was appointed to} consider the plans.}
    O'Connell \textbf{was appointed as} chairman.

    to arrange or decide a time or place for something to happen
    \textit{The committee appointed a day in June for celebrations.}
    \textit{Everyone assembled in the hall at the appointed time (=at the time that had been arranged).}

    \textit{a presidential appointee}

    self-appointed: giving yourself a responsibility, job, position etc without the agreement of other people, especially those you claim to represent – used to show disapproval

    well-appointed: a well-appointed room, house, or hotel has attractive furniture and all the equipment that you need
\end{DefWord}

\begin{DefWord}{disappoint, disappointed, disappointment}[disappoint]
    to make someone feel unhappy because something they hoped for did not happen or was not as good as they expected （使）失望:
    \textit{I hated to disappoint her.}

    \textbf{disappoint somebody's hopes/expectations/plans} to prevent something from happening that someone hoped for or expected
    \textit{The Berlin settlement of 1878 disappointed Russian hopes in the Balkans. 1878年的柏林条约使俄国在巴尔干的希望破灭了。}
\end{DefWord}

\begin{DefWord}{punctual, punctually, punctuality}[punctual]
    arriving, happening, or being done at exactly the time that has been arranged (on time)
    \textit{ She's always very punctual for appointments. 她一向准时赴约。}
    \textit{the punctual payment of invoices 准时结清费用清单}

    punctuality: the fact of happening or doing something at the agreed or correct time and not being late
    \textit{He insists on regular attendance and punctuality.}
\end{DefWord}

\begin{DefWord}{puncture}
    a small hole made accidentally in a tyre 〔轮胎上扎破的〕小孔，小洞
    \textit{She was cycling home when she had a puncture.}

    a small hole made by a sharp point, especially in someone's body
    \textit{puncture wounds}

    if a tyre punctures, or if you puncture it, a small hole appears in it
    \textit{A piece of glass punctured the back tyre.}

    to make a small hole in something
    \textit{One bullet punctured his lung.}

    to interrupt a period of silence by making a noise
    \textit{There was a stunned silence, punctured by shrill laughter.}

    to suddenly destroy someone's hopes or beliefs, making them feel unhappy, embarrassed, or confused
    \textit{He wasn't hurt, but his dignity was punctured. 他没有受伤，不过自尊受到了伤害。}
\end{DefWord}


\begin{DefWord}{punctuate, punctuation}[punctuate]
    to divide written work into sentences, phrases etc using commas, full stops etc

    to interrupt something, especially when this is repeated
    \textit{The silence was occasionally punctuated by laughter.}
    \begin{remark}
        Punctuate is usually passive in this meaning.
    \end{remark}
\end{DefWord}

\begin{DefWord}{pungent, pungently, pungentcy}[pungent]
    having a strong taste or smell
    \textbf{pungent smell/aroma/odour etc}

    \textbf{pungent speech} or \textbf{writing} is clever and direct, and usually criticizes someone or something strongly
    \textit{He expressed some fairly pungent criticisms.}
\end{DefWord}


\begin{DefWord}{compunction}
    a feeling that you should not do something because it is bad or wrong
    \textbf{have/feel no compunction about (doing) something}
    \textit{They used their tanks against the leftists \textbf{without compunction.} 他们肆无忌惮地使用坦克来对付左派人士。}
\end{DefWord}

\begin{DefWord}{acupuncture}
    a Chinese method of treating pain and illness using special thin needles that are pushed into the skin in particular parts of the body
\end{DefWord}



\subsection{preci}

\begin{RefWord}{praise}
    \textit{The mayor praised the rescue teams for their courage.}
\end{RefWord}

\begin{RefWord}{appreciate, appreciation}
    /ə'priːʃɪeɪt/

    to understand how serious or important a situation or problem is or what someone's feelings are (realize)
    \textbf{appreciate the significance/importance/value of something}
    \textit{He did not fully appreciate the significance of signing the contract.}


    used to thank someone in a polite way or to say that you are grateful for something they have done
    \textit{I appreciate your concern, but honestly, I'm fine. 谢谢你关心，不过说真的，我很好。}

    to understand how good or useful someone or something is
    \textit{Her abilities are not fully appreciated by her employer.}

    to gradually become more valuable over a period of time (opposite \ref{depreciate}\textbf{depreciate})
    \textit{Most investments are expected to appreciate at a steady rate.}
\end{RefWord}

\begin{RefWord}{precious, preciously, preciousness}
\end{RefWord}

\begin{RefWord}{appraise, appraisal}[appraise]
    to officially judge how successful, effective, or valuable something is (evaluate)
    \textit{Greenpeace has been invited to appraise the environmental costs of such an operation.}

    to look carefully at someone or something to make an opinion about them
    \textit{His eyes appraised her face.}

    appraisal: a statement or opinion judging the worth, value, or condition of something 评价；估计；鉴定
    \textbf{appraisal of}
    \textit{It needed a calmer appraisal of her situation.}
\end{RefWord}

\begin{RefWord}{depreciate, depreciation, depreciative}[depreciate]
    to decrease in value or price
    \textit{New cars \textbf{depreciate in value} quickly.}

    to reduce the value of something over time, especially for tax purposes
    \textit{Company computers are depreciated at 50\% per year. 公司电脑每年的折旧率为50\%.}

    to make something seem unimportant
    \textit{those who depreciate the importance of art in education 贬低艺术在教育中重要性的那些人}

    depreciative: causing gradual diminishment in value.
    \textit{a depreciative effect on the currency}
    
    expressing a critical or disparaging opinion.
    \textit{a depreciative view of the ministry}

    \begin{remark}
        depreciative is rather rare
    \end{remark}
\end{RefWord}