\chapter{Sense and Sensibility}

\section{sens (to feel)}

\begin{DefWord}{sense}
\end{DefWord}

\begin{DefWord}{sensible, sensibly}
\end{DefWord}

\begin{DefWord}{sensitive, insensitive, sensitivity, sensitively, hypersensitive, oversensitive}[sensitive]
\end{DefWord}

\begin{remark}
    \textbf{Sensible} and \textbf{sensitive} are connected with two different meanings of sense.

    \textbf{Sensible} refers to your ability to make good judgements:
    \textit{She gave me some very sensible advice. 她给了我一些非常合理的建议。}
    \textit{It wasn't very sensible to go out on your own so late at night. 这么晚一个人单独外出是不太明智的。}

    \textbf{Sensitive} refers to how easily you react to things and how much you are aware of things or other people. 涉及反应和洞察力
    \textit{a soap for sensitive skin 敏感皮肤用的肥皂}
\end{remark}

\begin{DefWord}{sensibility}
\end{DefWord}

\begin{remark}
    \textbf{Sensible}, \textbf{sensitive}, \textbf{sensibility} are not the same.

    
\end{remark}

\begin{DefWord}{consensus}
\end{DefWord}

\begin{DefWord}{consent}
\end{DefWord}

\begin{DefWord}{sentence}
\end{DefWord}

\begin{DefWord}{senseless}
    having no meaning or purpose (pointless)
    \textit{senseless violence}

    unconscious
    \textit{He was beaten senseless. 他被打昏了。}

    not using good judgement
    \textit{The police blamed senseless drivers who went too fast. 警察责怪莽撞司机开快车。}
\end{DefWord}

\begin{DefWord}{nonsense}
    ideas, statements or beliefs that you think are silly or not true
    \textit{Reports that he has resigned are nonsense. 有关他已经辞职的报道是无稽之谈。}
    \textit{You're talking nonsense! 你在胡说八道！}
    \textit{It's nonsense to say they don't care. 说他们不在意那是瞎扯。}

    spoken or written words that have no meaning or make no sense
    \textit{Most of the translation he did for me was complete nonsense.}

    silly or unacceptable behaviour
    \textit{The new teacher won't stand for any nonsense. 这位新教师不会容忍任何无礼行为}

    \textbf{make (a) nonsense of something}
    to reduce the value of something by a lot; to make something seem silly
    \textit{If people can bribe (to give somebody money or something valuable in order to persuade them to help you, especially by doing something dishonest) police officers, it makes a complete nonsense of the legal system. 如果人们可以收买警察，法律体系就会变得一文不值}
\end{DefWord}

\begin{remark}
    \textbf{Nonsense} and \textbf{senseless} are not the same.
\end{remark}

\begin{DefWord}{sensation, sensational}[sensation]
    a feeling that you get when something affects your body 感觉；知觉
    \textit{a tingling/burning sensation 刺痛/烧灼感}

    the ability to feel through your sense of touch
    \textit{She seemed to have lost all sensation in her arms.}

    a general feeling or impression that is difficult to explain; an experience or a memory
    \textit{When I arrived, I had the sensation that she had been expecting me.}

    very great surprise, excitement, or interest among a lot of \textit{people; the person or the thing that causes this surprise
    News of his arrest \textbf{caused a sensation}. 他被捕的消息引起了轰动。}

    sensational: causing great surprise, excitement, or interest
    \textit{The result was a sensational 4–1 victory.}

    (disapproving) trying to get your interest by presenting facts or events as worse or more shocking than they really are
    \textit{sensational news stories}

    extremely good; wonderful
    \textit{You look sensational in that dress!}
\end{DefWord}

\section{sent (to feel)}

\begin{DefWord}{sentiment, sentimental, sentimentally}[sentiment]
    a feeling or an opinion, especially one based on emotions
    \textit{the spread of nationalist sentiments 民族主义情绪的传播}

    feelings of sympathy, romantic love, being sad, etc. which may be too strong or not appropriate
    \textit{There was no fatherly affection, no display of sentiment.}

    sentimental: connected with your emotions, rather than reason
    \textit{He has a strong sentimental attachment to the place.}
    \textit{He wasn't the sort of person who kept things for \textbf{sentimental reasons}.}
    \textit{The rings that were stolen were of \textbf{great sentimental value} (=important because of your feelings or memories relating to them).}
    \textit{a \textbf{sentimental journey} to the place of his birth}

    (often disapproving) producing emotions such as sympathy, romantic love, or being sad, which may be too strong or not appropriate; feeling these emotions too much
    \textit{He's not the sort of man who gets \textbf{sentimental about} old friendships.}
\end{DefWord}

\begin{DefWord}{assent, dissent, dissenting, dissenter, dissension, dissentient}[assent]
    assent (to something) official agreement to or approval of 
    \textit{The director has \textbf{given her assent} to the proposals.}
    \textit{The bill passed in Parliament has now \textbf{received (the) Royal Assent} (= been approved by the king/queen).}

    \textbf{assent (to something) | (+ speech)} to agree to a request, an idea or a suggestion
    \textit{Nobody would assent to the terms they proposed.}

    dissent: the fact of having or expressing opinions that are different from those that are officially accepted
    \textit{political/religious dissent}

    the offence of openly disagreeing with the referee's decision
    \textit{He was sent off for dissent. 他因为不服从裁判而被罚下场。}

    a statement by a judge giving their reasons for disagreeing with the other judges in a law case 〔讼案中某法官对其他法官的意见所提出的〕异议﹐不同意见

    to say that you disagree with an official decision or accepted opinion  〔对官方决定或公认观点〕持异议﹐不同意
    \textbf{dissent from} \textit{There are some \textbf{dissenting voices} (=people who do not agree) among the undergraduates.}
\end{DefWord}

\begin{RefWord}{resent, resentment, resentful}
    resent (v): to feel bitter or angry about something, especially because you feel it is unfair

    resent something/somebody
    \textit{I resent something/somebody I \textbf{deeply resented} her criticism.}

    resent doing something
    \textit{He \textbf{bitterly resents} being treated like a child.}

    resent somebody doing something
    \textit{he resented \textbf{him} \textbf{making} all the decisions.}
\end{RefWord}

\section{pathy (to feel)}

\begin{RefWord}{sympathy}
    the feeling of being sorry for somebody; showing that you understand and care about somebody's problems

    \textbf{sympathy for somebody} to express/feel sympathy for somebody
    \textit{I \textbf{have no sympathy} for Jan—it's all her own fault.}

    \textit{May we \textbf{offer our} deepest \textbf{sympathies} on the death of your wife.}

    \textit{ I would like to \textbf{extend our sincere sympathies} to his family at this sad time.}

    the act of showing support for or approval of an idea, a cause, an organization, etc.
    \textbf{in sympathy with somebody/something} 
    \textit{The seamen went on strike in sympathy with (= to show their support for) the dockers.}

    friendship and understanding between people who have similar opinions or interests
    \textit{There was no personal sympathy between them. 他们个人之间全无相投之处。}
\end{RefWord}

\begin{DefWord}{telepathy}
    the direct communication of thoughts or feelings from one person to another without using speech, writing, or any other normal method
\end{DefWord}

\begin{DefWord}{apathy}
    /ˈæpəθi/

    the feeling of not being interested in or enthusiastic about something, or things in general

    \textit{There is \textbf{widespread apathy} among the electorate. 选民普遍态度冷淡。}
    \textbf{public/political/student apathy}
\end{DefWord}

\begin{DefWord}{antipathy}
    /ænˈtɪpəθi/

    \textbf{antipathy (between A and B) | antipathy (to/toward(s) somebody/something)} a strong feeling of dislike

    \textit{\textbf{personal/mutual antipathy} 个人／相互反感}
    \textit{a \textbf{growing antipathy} towards the idea}
\end{DefWord}

\begin{DefWord}{empathy}
    the ability to understand another person's feelings, experience, etc.

    \textbf{empathy (with somebody/something)} 
    \textit{the writer's imaginative empathy with his subject作者在想象中与笔下的人物情感共鸣}
 
    \textbf{empathy (for somebody/something) }
    \textit{empathy for other people's situations 对他人所处境况的同情}

    \textbf{empathy (between A and B)} 
    \textit{The empathy between the two women was obvious.}
\end{DefWord}

\section{rat, reck, rack, rat (to reason)}

\begin{DefWord}{reckon}
    \textbf{reckon (that)… (especially British English, informal)} to think something or have an opinion about something
    \textit{He'll be famous one day. \textbf{What do you reckon} (= do you agree)?}

    \textbf{be reckoned} to be generally considered to be something
    \textit{Children are \textbf{reckoned to be} more sophisticated nowadays.}
    \textit{It was generally reckoned a success.}

    (British English, informal) expect to do something
    \textit{We reckon to finish by ten.}

    to calculate an amount, a number, etc.

    \textbf{reckon something} 
    \textit{I could see him reckoning the cost as I spoke. 我说话的时候，可以看到他在计算费用。}

    \textbf{be reckoned at something} \textit{The age of the earth is reckoned at about 4.6 billion years. 地球的年龄估计约为46亿年。}
    \textit{My debts were reckoned at \$12 000. 我的债务估计为12 000美元。}

    \textbf{reckon (that)…} \textit{They reckon (that) their profits are down by at least 20\%.他们估计利润至少下降了 20\%。}

    \textbf{it is reckoned that…} It is generally reckoned that about half of all job vacancies are never advertised publicly. 人们普遍认为，所有职位空缺中约有一半从未公开刊登广告。

    \textbf{be reckoned to do something} \textit{The journey was reckoned to take about two hours. 路上估计要花大约两个小时。}
\end{DefWord}

\begin{DefWord}{rack}
    rack one's brain
\end{DefWord}

\begin{DefWord}{rat}
\end{DefWord}

\begin{DefWord}{read}
\end{DefWord}

\begin{DefWord}{reason}
\end{DefWord}

\begin{DefWord}{ration}
    a fixed amount of food, fuel, etc. that you are officially allowed to have when there is not enough for everyone to have as much as they want, for example during a war
\end{DefWord}

\begin{DefWord}{rational, rationally, rationality, rationalize}[rational]
    /ˈræʃnəlaɪz/
    based on reason rather than emotions
\end{DefWord}

\begin{DefWord}{ratify}
    \textbf{ratify something} to make an agreement officially or legally valid by voting for or signing it
    \textit{The treaty was ratified by all the member states.}
\end{DefWord}

\begin{DefWord}{ratio}
    the relationship between two groups of people or things that is represented by two numbers showing how much larger one group is than the other
    \textit{The ratio of nursing staff to doctors is 2:1 (two to one).}
\end{DefWord}

\section{put (to think)}

\begin{DefWord}{compute}
\end{DefWord}

\begin{DefWord}{computer}
\end{DefWord}

\begin{DefWord}{computerize}
\end{DefWord}

\begin{DefWord}{dispute}
\end{DefWord}

\begin{DefWord}{reputation}
\end{DefWord}



\section{cert, crit (separate, to judge)}

\begin{DefWord}{criteria, criterion}[criterion]
\end{DefWord}

\begin{DefWord}{criticize, critical, criticism, critic}[criticize]
\end{DefWord}

\begin{DefWord}{hypocrite}
\end{DefWord}

\begin{DefWord}{certify, certificate, certification}[certify]
\end{DefWord}

\begin{DefWord}{concert}
\end{DefWord}

\begin{DefWord}{certainly}
\end{DefWord}

\begin{DefWord}{certain, uncertain, certainty}
\end{DefWord}

\begin{DefWord}{ascertain}
\end{DefWord}