\chapter{Other New Words}

\begin{DefWord}{bombard}
    to attack a place for a long time using large weapons, bombs etc
    \textit{I had been in action, bombarding the Normandy coast. 我参加过轰炸诺曼底海岸的行动。}

    to do something too often or too much, for example criticizing or questioning someone, or giving too much information
    \textbf{bombard somebody with something}
    \textit{The office was bombarded by telephone calls.}
    \textit{Today we are bombarded with advice on what to eat and what to avoid.}

\end{DefWord}

\section{praise}

\begin{itemize}
    \item \textbf{praise}
    \item \textbf{congratulate}
    \item \textbf{compliment}
    \item \textbf{flatter} to praise someone in order to please them or get something from them, even though you do not mean it
    \textit{He had persuaded her to buy it by flattering her and being charming.}
    \item \textbf{enthuse about something} to talk about something you enjoy or admire in an excited way, and say that it is very good. Rave is rather informal, whereas enthuse is much more formal and is used mainly in written English \textit{She enthused about the joys of motherhood. 她滔滔不绝地诉说着为人母的喜悦。}
    \item \textbf{rave about something}
    \item \textbf{applaud}
    \item \textbf{commend} to praise someone or something, especially officially \textit{After the battle, Andrew Jackson commended him for 'his courage and fidelity'.}
    \item \textbf{hail somebody as something} to describe someone or something in a way that shows you have a very good opinion of them, especially in newspapers, on television reports etc \textit{The book was hailed as a masterpiece.}
\end{itemize}