\section{A, a}

\begin{DefWord}{agenda}
\end{DefWord}

\begin{DefWord}{agency}
\end{DefWord}

\begin{DefWord}{agent}
\end{DefWord}

\begin{DefWord}{aggress, aggressive, aggressor}[aggress]
\end{DefWord}

\begin{DefWord}{ambulance}
\end{DefWord}

\begin{DefWord}{ambulate} 
    ambulate /ˈæm byəˌleɪt/
    
    to walk about or move from place to place.
\end{DefWord}

\begin{DefWord}{ambulant} 
    ambulant /ˈæmbjələnt/
    
    (of a patient) able to walk; not having to stay in bed
\end{DefWord}

\begin{DefWord}{audio}
\end{DefWord}

\begin{DefWord}{audience}
\end{DefWord}

\begin{DefWord}{audition} 
    My  niece  was admitted  to  the Juilliard School of Music  in  America. But before that she was asked to attend an audition.
\end{DefWord}

\begin{DefWord}{auditorium}
\end{DefWord}

\begin{DefWord}{audible, inaudible}[audible]
    The audio-visual equipment there  is  magnificent that even  in the  farthest seat the music is still audible.
\end{DefWord}


\begin{DefWord}{aggress, aggressive, aggressor}[aggress]
\end{DefWord}

\begin{DefWord}{agent}
\end{DefWord}

\begin{DefWord}{apartment}
    a set of rooms on one floor of a large building, where someone lives

    a room or set of rooms used by an important person such as a president
    \textit{ I had never been in the prince's private apartments before.}
\end{DefWord}

\begin{DefWord}{apart}
    \textit{two miles/six feet etc apart}
    \textit{two days/three weeks/five years etc apart}

    if something comes apart, or you take it apart, it is separated into different pieces
    \textit{The whole thing \textbf{comes apart} so that you can clean it.}
    \textit{They \textbf{took} the engine \textbf{apart} to see what was wrong.}

    if you keep things apart, you keep them separate from each other
    \textit{I try to \textbf{keep} my work and private life as far \textbf{apart} as possible.}

    if people are apart, they are not together in the same place, or not having a relationship with each other
    \textit{The children have never been apart before.}

    \textbf{fall apart}
    if something falls apart, it breaks into different pieces;
    if something is falling apart, it is in very bad condition
    \textit{He drives around in an old car that's falling apart.}

    \textbf{be torn apart} if a marriage, family etc is torn apart, it can no longer continue because of serious difficulties
    \textit{The play portrays a good marriage torn apart by external forces.}

    \textbf{be worlds/poles apart} if people, beliefs, or ideas are worlds or poles apart, they are completely different from each other
    \textit{I realized we were still worlds apart. 我意识到我们之间仍有天壤之别。 }

    \textbf{grow/drift apart} if people drift or grow apart, their relationship slowly becomes less close
    \textit{Lewis and his father drifted apart after he moved to New York.}

    \textbf{joking apart} used to say that you want to say something
    seriously

    \textbf{somebody/something apart} except for someone or something
    \textit{The car industry apart, most industries are now seeing an improvement in their economic performance.}

    \textbf{set somebody/something apart} to make someone or something different from other people or things
    \textit{Her unusual lifestyle set her apart as a child.}
\end{DefWord}

\begin{DefWord}{apportion, apportionment}[apportion]
    to decide how something should be shared among various people

    \textit{It's not easy to \textbf{apportion blame} (=say who deserves to be blamed) when a marriage breaks up.}
    \textit{Court costs were equally apportioned between them.}
\end{DefWord}

\begin{DefWord}{apprehend, apprehension, apprehensive}[apprehend]
    arrest (someone) for a crime.
    $\star$"\textit{a warrant was issued but he has not been apprehended}";
    
    (old-fashioned) understand or perceive.
    "\textit{great art invites us to apprehend beauty}";to be apprehensive, suspicious, or fearful; fear.

    apprehensive: 担心 We'd been a little {apprehensive} about their visit.
\end{DefWord}

\begin{DefWord}{attain, attainment}[attain]
    sense of attainment
\end{DefWord}

\begin{DefWord}{abstain}
    抑制
    e.g. \textit{The man tries so hard to abstain from drinking.}
    
    戒绝,  弃权
    e.g. \textit{When you are in China, will you have to abstain from voting in your country?}
    \textit{Pilots must abstain from alcohol for 24 hours before flying.}
\end{DefWord}

\begin{DefWord}{abstract, abstraction, abstractly}[abstract]
    based on general ideas or principles rather than specific examples or real events (syn theoretical)

    existing only as an idea or quality rather than as something real that you can see or touch (opp concerte)

    a painting, design etc which contains shapes or images that do not look like real things or people抽象画；抽象设计；抽象派作品

    a short written statement containing only the most important ideas in a speech, article etc
    
    \textbf{in the abstract} considered in a general way rather than being based on specific details and examples

    to write a document containing the most important ideas or points from a speech, article etc

    (formal) to remove something from somewhere
\end{DefWord}

\begin{DefWord}{attract, attraction, attractive}[attract]
\end{DefWord}

\begin{DefWord}{avert}
    to prevent something unpleasant from happening
    \textit{The tragedy could have been averted if the crew had followed safety procedures.}

    \textbf{avert your eyes/gaze etc} 
    to look away from something so that you do not see it
    \textit{Henry averted his eyes as she undressed.}

\end{DefWord}

\begin{DefWord}{adversity}
    a situation in which you have a lot of problems that seem to be caused by bad luck
    \textit{his courage in the face of adversity}
\end{DefWord}

\begin{DefWord}{adversary}
    a country or person you are fighting or competing against 对手, 敌手 (SYN opponent)
\end{DefWord}

\begin{DefWord}{aspire}
    to desire and work towards achieving something important
    追求, 渴望, 有志于

    \textbf{aspire to}
    \textit{college graduates aspiring to careers in finance}

    \textbf{aspire to do something}
    \textit{At that time, all serious artists aspired to go to Rome.}
\end{DefWord}

\begin{DefWord}{advocate}
    to publicly support a particular way of doing something
    \textit{Those who advocate for doctor-assisted suicide say the terminally ill should not have to suffer.}

    someone who publicly supports someone or something
    \textit{She's a passionate advocate of natural childbirth.}
\end{DefWord}

\begin{DefWord}{acclaim, acclaimation}[acclaim]
    to praise someone or something publicly
\end{DefWord}

\begin{DefWord}{autobiography, autobiographical, autobiographer}[autobiography]
    autobiographical /ˌɔːtəbaɪəˈɡræfɪkəl/

    an autobiographical novel (=one based on the author's own experiences) 自传体小说
\end{DefWord}

\begin{DefWord}{antibiotics}
    a drug that is used to kill bacteria and cure infections 抗生素
\end{DefWord}

\begin{DefWord}{animate, inanimate}[animate]
    anim (soul) + ate (give) = give sth a soul

    to give life or energy to something 赋予…生命；使有生气[活力]:
    \textit{Laughter animated his face for a moment.}

    living 有生命的，活的 OPP  inanimate
    animate beings 生物 

    \textbf{animate something} to make models, toys, etc. seem to move in a film/movie by rapidly showing slightly different pictures of them in a series, one after another
\end{DefWord}

\begin{DefWord}{animal}
\end{DefWord}

\begin{DefWord}{animism}
    泛灵论，又称万物有灵论，是一种认为天地万物-动物、植物、环境、天气，乃至言词、画像、建筑或其他人工产物-都是有灵魂、能够思考和获取经验的主体，并且能够操纵或影响其他自然现象乃至人类社会的世界观。 它亦是目前已知最古老的信仰系统，在世界各地的传统文化中都能找到其踪影。 
\end{DefWord}

\begin{DefWord}{animosity}
    strong dislike or hatred
    \textit{There is no personal animosity between the party leaders. She felt a certain amount of animosity towards him.}
\end{DefWord}

\begin{DefWord}{abhor, abhorrent}[abhor]
    to hate a kind of behaviour or way of thinking, especially because you think it is morally wrong 厌恶，憎恶〔某种行为或思想方式〕
 \textit{I abhor discrimination of any kind. 我厌恶任何一种歧视。 }
\end{DefWord}

\begin{DefWord}{abduct, abduction, abductor, abductee}[abduct]
    to take someone away by force劫持，绑架 (SYN  kidnap)
    \textit{The diplomat was abducted on his way to the airport.  外交官在去机场途中遭绑架。 }

    abductor: a person who abducts somebody
\end{DefWord}