\section{C, c}

\begin{DefWord}{concur}
    to agree with someone or have the same opinion as them
    \textit{The committee largely concurred with these views.}
\end{DefWord}

\begin{DefWord}{concurrent, concurrency}[concurrent]
    existing or happening at the same time
    \textit{The exhibition reflected concurrent developments abroad.}
    concurrent with
    \textit{My opinions are concurrent with yours.}
\end{DefWord}

\begin{DefWord}{course}
    if a liquid or electricity courses somewhere, it flows there quickly
    \textit{Tears coursed down his cheeks.}

    if a feeling courses through you, you feel it suddenly and strongly
    \textit{His smile sent waves of excitement coursing through her.}

    a period of time or process during which something happens
    \textit{During the course of our conversation, it emerged that Bob had been in prison.}

    take/run its course: the usual or natural way that something changes, develops, or is done
    \textit{It seems the boom in World Music has run its course.}
\end{DefWord}

\begin{DefWord}{contradict, contradiction, contradictory}[contradict]
\end{DefWord}

\begin{DefWord}{contractor}
    See \ref{contract}.

    a person or company that agrees to do work or provide goods for another company
\end{DefWord}


\begin{DefWord}{counterpart}
    someone or something that has the same job or purpose as someone or something else in a different place
    \textit{Belgian officials are discussing this with their French counterparts.}
\end{DefWord}

\begin{DefWord}{compass}
\end{DefWord}

\begin{DefWord}{comprehend, comprehension, comprehensible}[comprehend]
    comprehensible input
\end{DefWord}

\begin{DefWord}{comprehensive}
    comprehensive introduction
\end{DefWord}

\begin{DefWord}{comprise}
    \textit{The house \textbf{comprises} two bedrooms, a kitchen, and a living room.} 
    
    \textit{The committee \textbf{is comprised of} well-known mountaineers. }
    
    \textit{Women \textbf{comprise} a high proportion of part-time workers.} 
    
    \textit{Food exports are very important, \textbf{comprising} 74\% of the total.}
\end{DefWord}

\begin{DefWord}{consequent, consequence}[consequent]
    something that happens as a result of a particular action or set of conditions; 
    
    (\textit{rare}) people of consequence; 
    
    \textbf{of little/no/any etc consequence} formal not very important or valuable
\end{DefWord}

\begin{DefWord}{consecutive}
   \textit{ It had rained for four consecutive days.}

    \textit{Can they win the title for the third consecutive season?}
\end{DefWord}

\begin{DefWord}{contract, contraction}[contract]
    /ˈkɒntrækt/ noun, /kənˈtrækt/ verb

    an official agreement between two or more people, stating what each will do

    \textbf{contract with/between}
    \textit{Tyler has agreed a seven-year contract with a Hollywood studio.}

    \textbf{contract to do sth}
    \textit{a three-year contract to provide pay telephones at local restaurants}

    \textbf{on a contract/under contract}
    \textit{Employees who refuse to relocate are in breach of contract} (=have done something not allowed by their contracts).


    \textbf{subject to contract}: if an agreement is subject to contract, it has not yet been agreed formally by a contract

    to become smaller or narrower
    \textit{Metal contracts as it cools.}

    to get an illness
    \textit{Two-thirds of the adult population there have contracted AIDS.}

    contraction: a very strong and painful movement of a muscle, especially the muscles around the womb (the part of a woman's or female animal's body where her baby grows before it is born 子宫 SYN  uterus) during birth
\end{DefWord}

\begin{DefWord}{concise, concisely, conciseness}[concise] 
\end{DefWord}

\begin{DefWord}{compel,  compulsion}[compel]
    to force someone to do something:
    \textit{The law will compel employers to provide health insurance.}

    (formal) to make people have a particular feeling or attitude
    \textit{His performance compelled the audience's attention.}
\end{DefWord}

\begin{DefWord}{convert, convertible}[convert]
    to change something into a different form, or to change something so that it can be used for a different purpose or in a different way

    convert sth to/into sth
    \textit{They converted the spare bedroom into an office.}

    \textit{a 19th-century \textbf{converted barn}} (=barn changed into a house)

    to change into a different form, or change into something that can be used for a different purpose or in a different way 改建；改装；改造；转换

    \textbf{convert to/into}
    to persuade someone to change to a different religion
    \textit{convert somebody to something
    European missionaries converted thousands to Christianity. 欧洲的传教士使成千上万的人皈依了基督教。 }

    to change to a different set of ideas, principles, or ways of doing something
    \textit{people who have recently converted to vegetarianism}
\end{DefWord}

\begin{DefWord}{controversial, controversially, controversy}[controversial]
\end{DefWord}

\begin{DefWord}{circumspect}
    thinking carefully about something before doing it, in order to avoid risk (cautious)
\end{DefWord}

\begin{DefWord}{conspire, conspiracy}[conspire]
    conspiracy /kənˈspɪrəsi/

    to secretly plan with someone else to do something illegal

    \textbf{conspire (with somebody) to do something}
    \textit{All six men admitted conspiring to steal cars.}

    \textbf{conspiracy of silence} an agreement not to talk about something, even though it should not be a secret
    \textit{There's often a conspiracy of silence surrounding bullying in schools.}

    \textit{He was charged with \textbf{conspiracy to} commit criminal damage.}

    \textit{There were many conspiracy theories (=beliefs that something is the result of a conspiracy) surrounding Princess Diana's death. 围绕戴安娜王妃之死有许多阴谋论。 }
\end{DefWord}

\begin{DefWord}{convivial}
    friendly and pleasantly cheerful
    \textit{a convivial atmosphere}
\end{DefWord}

\begin{DefWord}{commit, commitment}[commit]
    to do something wrong or illegal

    \textbf{commit murder/rape/arson etc}

    \textbf{commit suicide} to kill yourself deliberately

    \textbf{commit adultery} if a married person commits adultery, they have sex with someone who is not their husband or wife

    to say that someone will definitely do something or must do something
    \textbf{commit somebody to doing something}
    \textit{He has clearly committed his government to continuing down the path of economic reform. 他明确地作出保证，他的政府会继续在经济改革的道路上走下去。 }

    \textit{I'd \textbf{committed myself} and there was no turning back.}

    \textbf{commit yourself to (doing) something} 
    \textit{The banks have \textbf{committed themselves to boosting} profits by slashing costs.}

    to give someone your love or support in a serious and permanent way
    \textit{Anna wants to get married, but Bob's not sure he wants to commit.}

    to decide to use money, time, people etc for a particular purpose
    \textit{A lot of money has been committed to this project.}

    to send someone to be tried in a court of law
    \textit{The two men were \textbf{committed for trial} at Bristol Crown Court.}

    to order someone to be put in a hospital or prison
    \textit{The judge \textbf{committed him to prison} for six months.}
\end{DefWord}

\begin{DefWord}{compromise}
\end{DefWord}

\begin{DefWord}{conduct, conductor}[conduct]
    verb /kənˈdʌkt/, noun  /ˈkɒndʌkt/ 
    to carry out a particular activity or process, especially in order to get information or prove facts 〔尤指为获取信息或证实某事时〕进行；实施；执行
    \textit{We are \textbf{conducting a survey} of consumer attitudes towards organic food.}

    \textbf{conduct an experiment/a test}
    \textit{Is it really necessary to conduct experiments on animals?}

    to stand in front of a group of musicians or singers and direct their playing or singing

    \textbf{conduct yourself} formal to behave in a particular way, especially in a situation where people judge you by the way you behave 表现，为人:
    \textit{The players conducted themselves impeccably, both on and off the field.}


    if something conducts electricity or heat, it allows electricity or heat to travel along or through it 传导 $\rightarrow$ \textbf{conductor}
    \textit{Aluminum, being a metal, readily conducts heat.}

    to take or lead someone somewhere
    \textit{On arrival, I was conducted to the commandant's office. 到达以后，我被带到了指挥所。 }

    \textbf{conducted tour (of something)}（在某地）有导游陪同的参观旅行
    \textit{a conducted tour of Berlin (=a tour of a building, city, or area with someone who tells you about that place)}

    the way someone behaves, especially in public, in their job etc〔尤指在公共场合、工作岗位上等的〕行为，举止(behaviour)
    \textit{The Senator's conduct is being investigated by the Ethics Committee.}

    \textit{the Law Society's \textbf{Code of Professional Conduct} 法律协会的行业行为准则}

    \textit{his arrest for \textbf{disorderly conduct} (=noisy violent behaviour)他因妨害治安行为而遭逮捕}

    \textbf{conduct of something} the way in which an activity is organized and carried out
   \textit{complaints about the conduct of the elections}
\end{DefWord}