\section{D, d}

\begin{DefWord}{disconnect}
\end{DefWord}

\begin{DefWord}{distract, dictracting, distracted, distraction}[distract]
    distracting: taking your attention away from what you are trying to do
    \textit{distracting thoughts}

    distracted: somebody/something because you are worried or thinking about something else
    \textit{Luke looked momentarily distracted.}
\end{DefWord}

\begin{DefWord}{dialogue}
\end{DefWord}

\begin{DefWord}{department}
\end{DefWord}

\begin{DefWord}{doctor}
\end{DefWord}

\begin{DefWord}{detractor}
    See \ref{detract}.
\end{DefWord}

\begin{DefWord}{department}
    one of the groups of people who work together in a particular part of a large organization such as a hospital, university, company, or government
    \textit{the personnel department}

    an area in a large shop where a particular type of product is sold
    \textit{the toy department}
\end{DefWord}

\begin{DefWord}{depart, departure}[depart]
    to leave, especially when you are starting a journey

    depart this life formal to die

    to start to use new ideas or do something in a different way
    \textit{It's revolutionary music; it departs from the old form and structures.}

    to leave an organization or job
    \textit{the company's departing chairman}

    \textbf{departure from one place to another place}
\end{DefWord}

\begin{DefWord}{dissect, dissection, dissectible}[dissect]
    to cut up the body of a dead animal or person in order to study it

    to examine something carefully in order to understand it
    \textit{books in which the lives of famous people are dissected}

    to divide an area of land into several smaller pieces
    \textit{fields dissected by small streams}
\end{DefWord}

\begin{DefWord}{detain, detainer, detainee, detainment}[detain]
    to force someone officially to stay in a place
    \textit{A suspect has been detained by the police for questioning.}

    to delay someone for a short length of time
\textit{I'm sorry I'm late - I was unavoidably detained.}
\end{DefWord}

\begin{DefWord}{detract, detraction}[detract]
    \textbf{detract from something}
    to make something seem less good (OPP  enhance):
    \textit{One mistake is not going to detract from your achievement.}
\end{DefWord}

\begin{DefWord}{decide}
    de 加强
\end{DefWord}

\begin{DefWord}{dispel}
    make something go away, especially a belief, idea, or feeling
    \textit{We want to \textbf{dispel} the \textbf{myth} that you cannot eat well in Britain.}

    Syn $\rightarrow$ \ref{expel}.
\end{DefWord}

\begin{DefWord}{devolve}
    if you devolve responsibility, power etc to a person or group at a lower level, or if it devolves on them, it is given to them（将）〔责任、权力等〕下放[转交， 委派]

    \textbf{devolve something to somebody/something}
    \textit{The federal government has devolved responsibility for welfare to the states.}

    \textbf{devolve on/upon}
    \textit{Half of the cost of the study will devolve upon the firm.}

    if land, money etc devolves to someone, it becomes their property when someone else dies（将）〔土地、钱等在某人死后〕转移， 转让〔给某人〕 SYN  pass
\end{DefWord}

\begin{DefWord}{diverse, diversify}[diverse]
    if a business, company, country etc diversifies, it increases the range of goods or services it produces
    \textit{farmers forced to \textbf{diversify} away \textbf{from} their core business}

    \textit{The company is planning to \textbf{diversify} \textbf{into} other mining activities.}

    to change something or to make it change so that there is more variety
    \textit{User requirements have diversified over the years.}

    to put money into several different types of investment instead of only one or two 投资多元化， 进行分散化投资
    \textit{Spread the risk by diversifying into dollar bonds. 购买美元债券进行多种投资， 以分散风险。 }

\end{DefWord}

\begin{DefWord}{divert, diversion, diverting}[divert]
    to change the use of something such as time or money 改变…的用途
    \textbf{divert something into/to/(away) from etc something}
    \textit{The company should divert more resources into research.}

    to change the direction in which something travels 改变…的方向， 使转向
    \textbf{divert a river/footpath/road etc}
    \textit{Canals divert water from the Truckee River into the lake.}

    if you divert your telephone calls, you arrange for them to go directly to another number, for example because you are not able to answer them yourself for some time 转移〔电话〕:
    \textit{Remember to divert your phone when you are out of the office.}

    to deliberately take someone's attention from something by making them think about or notice other things〔故意〕转移， 分散〔别人的注意力〕
    \textbf{divert (somebody's) attention (away from somebody/something)}
    T\textit{he crime crackdown is an attempt to divert attention from social problems.}
 
    to amuse or entertain someone 使消遣， 给…解闷， 供…娱乐

\end{DefWord}


\begin{DefWord}{disclaim}
    to state, especially officially, that you are not responsible for something, that you do not know about it, or that you are not involved with it (deny)
    \textit{Martin disclaimed any responsibility for his son's actions.}
\end{DefWord}

\begin{DefWord}{deter, deterrent}[deter]
    to stop someone from doing something, by making them realize it will be difficult or have bad results 威慑住，吓住，使却步 $\rightarrow$  deterrent:

    \textbf{deter somebody from (doing) something}
    \textit{The security camera was installed to deter people from stealing.}

    something that makes someone less likely to do something, by making them realize it will be difficult or have bad results 遏制物，威慑物，威慑力量:
    \textit{The small fines for this type of crime do not \textbf{act as much of a deterrent}.}

    \textbf{nuclear deterrent} the nuclear weapons that a country has in order to prevent other countries from attacking it
\end{DefWord}

\begin{DefWord}{despair}
\end{DefWord}

\begin{DefWord}{desperate, desperately, desperation, desperado}
    willing to do anything to change a very bad situation, and not caring about danger
    \textit{Time was running out and we were \textbf{getting desperate}. 时间越来越少，我们越来越感到绝望。 }

    needing or wanting something very much
    \textit{The team is \textbf{desperate for} a win.这支球队急需一场胜利。 }

    \textbf{a desperate situation} is very bad or serious

    desperado:  a violent criminal who is not afraid of danger 亡命之徒，暴徒
\end{DefWord}

\begin{DefWord}{deject, dejected, dejection}[deject]
    (rare) make sad or dispirited; depress.

    dejected: unhappy, disappointed, or sad
    \textit{The unemployed stood at street corners, dejected.}
\end{DefWord}

\begin{DefWord}{dismiss, dismissal}[dismiss]
    to refuse to consider someone's idea, opinion etc, because you think it is not serious, true, or important
    \textit{The government has dismissed criticisms that the country's health policy is a mess.}

    \textbf{dismiss something as something}
    \textit{He just laughed and dismissed my proposal as unrealistic.}

    \textbf{dismiss somebody from something}
    \textit{ Bryant was unfairly dismissed from his post.}

    to tell someone that they are allowed to go, or are no longer needed
    \textit{The class was dismissed early today.}

    if a judge dismisses a court case, he or she stops it from continuing
    \textit{The case was dismissed owing to lack of evidence. 由于证据不足，该案被驳回了。 }
\end{DefWord}

\begin{remark}
    In everyday British English, people usually say \textbf{sack} someone, and in everyday American English, people usually say \textbf{fire} someone, rather than use \textbf{dismiss}:
\end{remark}

\begin{DefWord}{deduce, deducible, deductive, deduction}[deduce]
    to use the knowledge and information you have in order to understand something or form an opinion about it 推论，推断，演绎

    \textbf{deduce that}
    \textit{From her son's age, I deduced that her husband must be at least 60. 从她儿子的年龄来推测，我想她丈夫肯定至少有60岁了。 }

    \textbf{deduce from}
    \textit{What did Darwin deduce from the presence of these species? 达尔文从这些物种的存在推断出了什么？}

    \textbf{deductive reasoning} 演绎推理

    deduction: the process of using the knowledge or information you have in order to understand something or form an opinion, or the opinion that you form
    \textit{Children will soon \textbf{make deductions} about the meaning of a word.}

    the process of taking away an amount from a total, or the amount that is taken away
    \textit{After deductions for tax etc, your salary is about £700 a month.扣除税款等之后，你的月薪大约有700英镑。 }
\end{DefWord}

\begin{DefWord}{duct}
    a pipe or tube that liquids, air, cables etc pass through
    \textit{Air is heated and then circulated through large ducts to all parts of the house.}

    a narrow tube in your body or in a plant that liquid passes through
    \textit{a tear duct 泪管}
\end{DefWord}

\begin{DefWord}{docent}
    someone who guides visitors through a museum, church etc (guide)
\end{DefWord}

\begin{DefWord}{doctoral}
    done as part of work for the university degree of doctor
    博士（学位）的:
    \textit{a doctoral thesis}
\end{DefWord}

\begin{DefWord}{doctorate}
    a university degree of the highest level 博士学位
    \textit{She received her \textbf{doctorate in history} in 1998. 她于1998年获得历史学博士学位。 }
\end{DefWord}


\begin{DefWord}{document}
\end{DefWord}

\begin{DefWord}{documentary}
    documentary films, programmes, photographs etc give or show information about a particular subject
    〔电影、电视、照片等〕纪录的，纪实的:
    \textit{documentary films}

    consisting of or written on documents
    文件的，文献的
    \textbf{documentary evidence/proof}
    \textit{One of the most useful sources of documentary evidence is maps.}
\end{DefWord}

\begin{DefWord}{doctrine}
    doctrine /ˈdɒktrɪn/,doctrinal /dɒkˈtraɪnl/

    a set of beliefs that form an important part of a religion or system of ideas
    信条，教义，主义，学说:
    \textit{traditional doctrines of divine power 传统的神力教义}
    \textit{Marxist doctrine 马克思主义学说}

    \textbf{Doctrine}  a formal statement by a government about its future plans〔政府未来政策的〕正式声明:
    \textit{the announcement of the Truman Doctrine杜鲁门主义的宣言}
\end{DefWord}

\begin{DefWord}{docile, indocile}[docile]
\end{DefWord}