\section{I, i}

\begin{DefWord}{insectcide}
    /ɪnˈsektɪsaɪd/
\end{DefWord}

\begin{DefWord}{impart, impartment}[impart]
    to give a particular quality to something
    \textbf{impart something to something}
    \textit{Use a piece of fresh ginger to impart a Far Eastern flavour to simple ingredients.}

    to give information, knowledge, wisdom etc to someone
    \textit{She had information that she couldn't wait to impart.}
\end{DefWord}

\begin{DefWord}{imparter}
    See \ref{impart}
\end{DefWord}

\begin{DefWord}{inside}
\end{DefWord}

\begin{DefWord}{invade}
\end{DefWord}

\begin{DefWord}{impede, impediment}[impede]
    impede /ɪmˈpiːd/,  impediment /ɪmˈpedəmənt/ 

    to make it difficult for someone or something to move forward or make progress
    \textit{One shouldn't impede another's progress.}

    im- 里面
\end{DefWord}

\begin{DefWord}{imprison}
    See \ref{prison}.
    to put in or as if in prison
\end{DefWord}

\begin{DefWord}{insect}
    any small creature with six legs and a body divided into three parts. Insects usually also have wings. Ants, bees and flies are all insects.
\end{DefWord}

\begin{DefWord}{insecticide,  insecticidal }[insecticide]

    a chemical substance used for killing insects

    insecticidal: connected with the use of chemicals to kill insects 
\end{DefWord}

\begin{DefWord}{intersect, intersection}[intersect]
    
    if two lines or roads intersect, they meet or go across each other
    \textit{Two or more lines intersect.}
    \textit{one line intersects another}

    to divide an area with several lines, roads etc
    \textit{The plain is intersected by a network of canals.}

    intersection: a place where roads, lines etc cross each other, especially where two roads meet
\end{DefWord}

\begin{DefWord}{invade}
\end{DefWord}


\begin{DefWord}{incise}
    to cut a pattern, word etc into something, using a sharp instrument
    \textit{an inscription incised in stone}
\end{DefWord}

\begin{DefWord}{incisor}
\end{DefWord}

\begin{DefWord}{impel}
    if something impels you to do something, it makes you feel very strongly that you must do it ($\rightarrow$ \ref{compel})

    \textit{The lack of democracy and equality impelled the oppressed to fight for independence.}
\end{DefWord}



\begin{DefWord}{introvert}
\end{DefWord}

\begin{DefWord}{imperial}
\end{DefWord}

\begin{DefWord}{imperialist}
\end{DefWord}

\begin{DefWord}{imperialism}
\end{DefWord}

\begin{DefWord}{inspire, inspiration, inspiring, inspirational}[inspire]
    to encourage someone by making them feel confident and eager to do something

    to breathe in 吸入〔空气〕

    inspirational: providing encouragement or new ideas for what you should do
    \textit{Jones proved an inspirational figure in Welsh rugby.}


    giving people a feeling of excitement and a desire to do something great 鼓舞人心的；启发灵感的 OPP  uninspiring:
    \textit{inspiring music}
\end{DefWord}

\begin{DefWord}{inhale}
    to breathe in air, smoke, or gas
\end{DefWord}

\begin{DefWord}{invoke}
\end{DefWord}

\begin{DefWord}{invigorate}
    if something invigorates you, it makes you feel healthier, stronger, and have more energy
    \textit{At my age, the walk into town is enough to invigorate me.}

    to make the people in an organization or group feel excited again, so that they want to make something successful
    \textit{Carey's hope was that the church would be renewed and invigorated.}
\end{DefWord}