\section{P, p}

\begin{DefWord}{preamble}
    preamble /priː'æmb(ə)l/

\textit{Harding gave him the news without preamble} (=without saying anything else before it)
\end{DefWord}

\begin{DefWord}{proceed}
\end{DefWord}

\begin{DefWord}{precede, preceding, precedence}[precede]
    precedence /ˈpresɪdəns/
    to happen or exist before something or someone, or to come before something else in a series

    to go somewhere before someone else
    \textit{The guard preceded them down the corridor.}

    precedence: when someone or something is considered to be more important than someone or something else, and therefore comes first or must be dealt with first (priority)
\end{DefWord}


\begin{DefWord}{predict, prediction, predictable, unpredictable}[predict]
\end{DefWord}

\begin{DefWord}{partner}
\end{DefWord}

\begin{DefWord}{progress}
    \textit{More and more people snore as their age progresses and it is harmful to their health.}

    \textit{make progress}
\end{DefWord}

\begin{DefWord}{prologue}
\end{DefWord}

\begin{DefWord}{participate, participation, participator}[participate]
    participator: 参与者、合作者
\end{DefWord}

\begin{DefWord}{partial, impartial, partially, partialness}[partial]
    not complete部分的, 不完全的:
    \textit{The exhibition was only a partial success.那次展会只获得部分成功. }
    \textit{a partial solution to traffic congestion in Oxford部分解决牛津地区交通拥堵问题的方法}

    be partial to something formal to like something very much
    \textit{I'm very partial to cream cakes.我特别喜欢吃奶油蛋糕. }

    unfairly supporting one person or one group against another 偏向一方的, 偏袒的, 不公平的 (OPP impartial)
\end{DefWord}

\begin{DefWord}{partner}
    to be someone's partner in a dance, game etc
    \textit{I used to partner him in tennis matches.}
    \textit{I am partnering Tina to give this lesson.}
    \textit{I am partnered Tina to give this lecture.}
\end{DefWord}

\begin{DefWord}{particular, particularly}[particular]
    [only before noun] a particular thing or person is the one that you are talking about, and not any other (certain, specific):
    \textit{In this particular case, no one else was involved.这件事没有其他人牵涉其中. }

    special or great:
    \textit{You should pay particular attention to spelling.你应该特别注意拼写. }
    
    \textbf{anything/nothing/something particular}
    \textit{I had nothing particular planned.我没有什么特别的计划. }

    very careful about choosing exactly what you like and not easily satisfied 讲究的；挑剔的, 吹毛求疵的 (SYN  fussy)
    
    \textbf{particular about}
    \textit{Marty's very \textbf{particular about} his food.}

\end{DefWord}

\begin{DefWord}{partake, partaker}[partake]
    to eat or drink something
    \textit{Grandmother likes to partake of a small glass of sherry before lunch.}

    to take part in an activity or event
    (SYN  participate)
    \textit{a woman's fundamental right to \textbf{partake in} club affairs}

    \textbf{partake in=take part in}

    \textbf{partake of something} 
    to have a certain amount of a particular quality有点…, 带有几分〔某种性质〕
\end{DefWord}

\begin{DefWord}{partition}
\end{DefWord}

\begin{DefWord}{passenger}
\end{DefWord}

\begin{DefWord}{passage}
    a long narrow area with walls on either side which connects one room or place to another
    \textit{My office is just along the passage.}

    a short part of a book, poem, speech, piece of music etc
    \textit{He read out a short passage from the Bible.}

    the movement of people or vehicles along a road or across an area of land
    \textit{The bridge isn't strong enough to allow the passage of heavy vehicles.}
\end{DefWord}

\begin{DefWord}{pass}
\end{DefWord}

\begin{DefWord}{pedal}
\end{DefWord}

\begin{DefWord}{pervade}
\end{DefWord}

\begin{DefWord}{proportion, proportions, proportional, disproportional}[proportion]
    \textit{The \textbf{proportion of} women graduates has increased in recent years.}

    \textit{The decision affects \textbf{a significant proportion} of the population.}

    proportional = in proportion

    disproportional = out of proportion


the proportion of something to something
\textit{What's the proportion of boys to girls in your class?}

in proportion to something
\textit{The rewards you get in this job are in direct proportion to the effort you put in.}

the correct or most suitable relationship between the size, shape, or position of the different parts of something
\textit{Builders must learn about scale and proportion.}

\textit{Reduce the drawing so that all the elements stay in proportion. 缩小这幅画以使各部分保持协调. }

in proportion to something
\textit{Her feet are small in proportion to her height.}

out of proportion with something
\textit{The porch is out of proportion with (=too big or too small when compared with) the rest of the house.}

proportions (plural):
the size or importance of something
\textit{The flu outbreak has reached epidemic proportions.}

\textit{of immense/huge/massive etc proportions}

\textit{For most of us, Scott was a hero of mythic proportions.}

the relative sizes of the different parts of a building, object etc
\textit{a building of classic proportions}

out of (all) proportion too big, great, or strong in relation to something（相对某事物来说）超出比例；与…不相称

\textbf{proportion to/with}

\textit{The fear of violent crime has now risen out of all proportion to the actual risk.对暴力犯罪的恐惧大大超出了实际的危险. }

\textbf{get/blow something out of proportion} 把事情看得过分严重
(=treat something as more serious than it really is)

\textit{Aren't you getting things rather out of proportion?}你是不是把事情想得太糟了？
\textit{The whole issue has been blown out of all proportion.}整件事被过分夸大了. 

keep something in proportion to react to a situation sensibly, and not think that it is worse or more serious than it really is 办事情[看问题]恰如其分；不把问题看得太糟[太过严重] $\rightarrow$ perspective:
\textit{Let's keep things in proportion.}我们别把事情看得太糟. 

sense of proportion the ability to judge what is most important in a situation区别轻重缓急的能力；主次观念

\textbf{have/keep/lose a sense of proportion}
\textit{You can protest by all means, but keep a sense of proportion.}你自然可以抗议, 但是要分清主次. 

technical equality in the mathematical relationship between two sets of numbers, as in the statement '8 is to 6 as 32 is to 24'比例〔如8:6 = 32:24〕 $\rightarrow$ ratio


\end{DefWord}



\begin{DefWord}{portion}
    a part of something larger, especially a part that is different from the other parts
    \textit{The front portion of the rocket breaks off}

    an amount of food for one person, especially when served in a restaurant (SYN  serving, helping)
    \textit{Do you have any children's portions?}

    to divide something into parts and give it to several people
    \textit{The money was portioned out among them.}
\end{DefWord}

\begin{DefWord}{previous}
\end{DefWord}

\begin{DefWord}{prison}
    a place of confinement(拘禁) especially for lawbreakers
\end{DefWord}

\begin{DefWord}{protract}
    to draw out or lengthen, especially in time; extend the duration of; prolong.
\end{DefWord}

\begin{DefWord}{prosecute, prosecution}[prosecute]
    to charge someone with a crime and try to show that they are guilty of it in a court of law

    \textit{The company is to be \textbf{prosecuted} under the Health and Safety Act.}
\end{DefWord}

\begin{DefWord}{persecute}
    to treat someone cruelly or unfairly over a period of time, especially because of their religious or political beliefs

    \textit{The Puritans (清教徒) left England to escape being persecuted. Like many celebrities, she complained of being persecuted by the press.}
\end{DefWord}

\begin{DefWord}{pervade}
    if a feeling, idea, or smell pervades a place, it is present in every part of it
    \textit{A spirit of hopelessness pervaded the country.}
\end{DefWord}

\begin{DefWord}{pesticide, pesticidal}[pesticide]
    Similar to \ref{insecticide}.
\end{DefWord}


\begin{DefWord}{precise, preciseness}[precise]
\end{DefWord}

\begin{DefWord}{propel}
    to move, drive, or push something forward
\end{DefWord}


\begin{DefWord}{propeller}
    a piece of equipment consisting of two or more blades that spin around, which makes an aircraft or ship move
\end{DefWord}

\begin{DefWord}{pervert}
    to change something in an unnatural and often harmful way
    \textit{Genetic scientists are often accused of perverting nature.}

    to influence someone so that they begin to think or behave in an immoral way 使走上邪路, 使堕落, 使变坏, 腐蚀
    \textit{TV violence perverts the minds of young children.电视暴力腐蚀了孩子们的心灵. }
\end{DefWord}

\begin{DefWord}{perspective}
    a way of thinking about something, especially one which is influenced by the type of person you are or by your experiences

    \textit{His father's death gave him a whole new \textbf{perspective on} life.}
    
    \textbf{from somebody's/a feminist/Christian/global etc perspective}
    \textit{The novel is written from a child's perspective.}

    \textit{Our work in Uganda and Romania adds a \textbf{wider/broader perspective}.}

    a sensible way of judging and comparing situations so that you do not imagine that something is more serious than it really is
    \textit{I think Viv's \textbf{lost} all \textbf{sense of perspective. 我认为维夫已不能明察事理. }}

    \textbf{get/keep something in perspective}
    \textit{The figures have to be \textbf{put into perspective}. 必须正确认识这些数字. }

    a method of drawing a picture that makes objects look solid and shows distance and depth, or the effect this method produces in a picture 透视（画）法；透视效果, 透视感
\end{DefWord}

\begin{DefWord}{prospect}[prospect]
    [countable, uncountable] the possibility that something will happen 可能性；希望
    \textbf{prospect of doing something}
    \textit{I see \textbf{no prospect} of things improving here.}
    \textit{There is \textbf{every prospect} (=a strong possibility) of the weather remaining dry this week.} 本周天气很有可能持续干燥. 
    
    \textbf{prospect for}
    \textit{There are good prospects for growth in the retail sector.} 零售行业有很好的发展前景. 

    \textbf{prospect that}
    \textit{There's a \textbf{real prospect} that England will not qualify for the World Cup.} 英格兰队很有可能进不了世界杯决赛圈. 

    a particular event which will probably or definitely happen in the future – used especially when you want to talk about how you feel about it

    \textbf{prospect of}
    \textit{The prospect of marriage terrified Alice.} 想到要结婚, 艾丽斯害怕极了. 
    
\textbf{daunting/exciting etc prospect} 可怕的/激动人心等的前景

\textbf{be excited/alarmed/concerned etc at the prospect (of something)}
 \textit{She wasn't exactly overjoyed at the prospect of looking after her niece.} 想到要照看侄女, 她并不怎么高兴. 

prospects [plural]: chances of future success 将来成功的机会, 前途, 前程:
 \textit{I had no job, no education, and \textbf{no prospects.}} 我没有工作, 没受过什么教育, 前途渺茫. 

\textbf{job/career prospects}
 \textit{Job prospects for graduates don't look good.}毕业生的就业前景看上去不妙. 

[countable] a person, job, plan etc that has a good chance of success in the future 有前途的人[工作, 计划等]

in prospect formal likely to happen in the near future 可能即将发生的:
 A new round of trade talks is in prospect.可能即将举行新一轮的贸易会谈. 
\end{DefWord}

\begin{DefWord}{perspire, perspiration}[perspire]
    if you perspire, parts of your body become wet, especially because you are hot or have been doing hard work 出汗, 流汗

    perspiration: liquid that appears on your skin when you are hot or nervous 汗, 汗水
\end{DefWord}

\begin{DefWord}{provoke, provocation, provocative}[provoke]
    provocation /ˌprɒvəˈkeɪʃən/ provocative /prəˈvɒkətɪv/


    to cause a reaction or feeling, especially a sudden on
    \textit{The decision to invade provoked storms of protest.}

    provoke debate/discussion

    provoke somebody into (doing) something
    \textit{She hopes her editorial will \textbf{provoke readers into} thinking seriously about the issue.}

    to make someone angry, especially deliberately
    \textit{The dog would not have attacked if it hadn't been provoked.}

    \textbf{provocative}  behaviour, remarks etc are intended to make people angry or upset, or to cause a lot of discussion

    \textit{a provocative act by a terrorist group 恐怖团体的挑衅行为}
    \textit{She was accused of being deliberately provocative. 她被指责故意挑衅. }

    provocative clothes, movements, pictures etc are intended to make someone sexually excited
    \textit{provocative images of young girls 少女们撩人的形象}
\end{DefWord}

\begin{DefWord}{proclaim}
    to say publicly or officially that something important is true or exists 宣布, 声明 $\rightarrow$ proclamation:
    \textit{The president proclaimed the republic's independence.}

    to show something clearly or be a sign of something
    \textit{The stripes on her uniform proclaimed her seniority. 制服上的条纹表明她的级别很高. }

\end{DefWord}

\begin{DefWord}{pusillanimous}
    /ˌpjuːsɪˈlænɪməs/
    
    frightened of taking even small risks
\end{DefWord}

\begin{DefWord}{prosper, prosperity, prosperous}[prosper]
\end{DefWord}

\begin{DefWord}{project, projection}[project]
    noun  /ˈprɒdʒekt/, verb /prəˈdʒekt/
    
    a carefully planned piece of work to get information about something, to build something, to improve something etc 项目；工程；计划；规划:
    
    to calculate what something will be in the future, using the information you have now预计，推断:
     \textit{The company projected an annual growth rate of 3\%. 该公司预计每年的增长率为3\%}. 
    
 \end{DefWord}
    
 \begin{DefWord}{produce, product, production, producer}[produce]
 \end{DefWord}

 \begin{DefWord}{photography, photograph, photographer}[photograph]
 \end{DefWord}