\section{R, r}

\begin{DefWord}{retain}
    \textit{We hope to \textbf{retain} all these beautiful moments in our memory.}
\end{DefWord}

\begin{DefWord}{retract, retractable}[retract]
    if you retract something that you said or agreed, you say that you did not mean it (SYN  withdraw):
    \textit{He confessed to the murder but later retracted his statement.}

    if part of a machine or an animal's body retracts or is retracted, it moves back into the main part
    \textit{The sea otter (海獭) can retract the claws on its front feet.}
\end{DefWord}

\begin{DefWord}{repel, repulsive, repellent}[repel]
    if something repels you, it is so unpleasant that you do not want to be near it, or it makes you feel ill使厌恶, 使反感 $\rightarrow$ :
    \textit{The smell repelled him}

    to make someone who is attacking you go away, by fighting them
    \textit{The army was ready to repel an attack.}

    to keep something or someone away from you:
    \textit{a lotion that repels mosquitoes}

    if two things repel each other, they push each other away with an electrical force (OPP attract)
    \textit{Two positive charges repel each other.}

    repellent: very unpleasant (repulsive)
    \textit{She found him physically repellent}

    \textbf{repellent to}
    \textit{The sight of blood is repellent to some people.}

\end{DefWord}

\begin{DefWord}{revolve, revolving, revolution}[revolve]
    to move around like a wheel, or to make something move around like a wheel, e.g. the windmill

    \textit{revolving door}

    \textbf{revolve around somebody/something}:
    to have something as a main subject or purpose
    
    \textit{She seems to think that the world \textbf{revolves around} her}

    to move in circles around something
    \textit{The Moon revolves around the Earth.}

    a \textbf{revolving} object is designed so that it turns with a circular movement

\end{DefWord}

\begin{DefWord}{revolt}
    反抗
\end{DefWord}

\begin{DefWord}{revert}
\end{DefWord}

\begin{DefWord}{rebel}
\end{DefWord}

\begin{DefWord}{retrospect}
    \textbf{in retrospect} thinking back to a time in the past, especially with the advantage of knowing more now than you did then

    \textit{In retrospect, I wonder if we should have done more.}
\end{DefWord}

\begin{DefWord}{respire, respiratory, respiration, artificial respiration}[respire]
    respiration /ˌrespəˈreɪʃən/ 

    to breathe呼吸

    artificial respiration
\end{DefWord}

\begin{DefWord}{revoke, revocable, irrevocable}[revoke]
\end{DefWord}

\begin{DefWord}{reclaim, reclamation}[reclaim]
    to get back an amount of money that you have paid = claim back
    \textit{You may be entitled to reclaim some tax.}

    to make an area of desert, wet land etc suitable for farming or building
    \textit{This land will be reclaimed for a new airport.}

    to get back something that you have lost or that has been taken away from you
    \textit{I want to reclaim the championship that I lost in 1999.}

    to obtain useful products from waste material
    \textit{You can reclaim old boards and use them as shelves.}

    \textbf{reclaim somebody (from something)} to rescue somebody from a bad or criminal way of life
\end{DefWord}

\begin{DefWord}{revive}
    /rɪˈvaɪv/

    to bring something back after it has not been used or has not existed for a period of time
    \textit{Local people have decided to revive this centuries-old tradition.}

    to become healthy and strong again, or to make someone or something healthy and strong again
    \textit{The economy is beginning to revive.}

    to produce a play again after it has not been performed for a long time
    \textit{A London theatre has decided to revive the 1950s musical 'In Town'. 伦敦的一家剧院决定重新排演20世纪50年代的音乐剧《在镇上》。 }
\end{DefWord}

\begin{DefWord}{reject, rejection, rejective}[reject]
    \textit{The proposal was firmly rejected. Their rejective attitude and blank rejection let us down.}
\end{DefWord}

\begin{DefWord}{remit, remittance}[remit]
    to send a payment 汇（款）
    \textit{Please remit payment by cheque.}

    to free someone from a debt or punishment 免除〔债务或处罚〕 $\rightarrow$  unremitting

    \textbf{remit something to somebody/something}
    to send a proposal, plan, or problem back to someone for them to make a decision about
    \textit{The court remitted the matter to the agency for reconsideration. 法庭将此事发回该机构作重新考虑。 }

    the particular piece of work that someone has been officially asked to deal with
    \textit{the remit of a senior member of staff}

    remittance: an amount of money that you send to pay for something

    when you send money
    \textit{We will forward the goods on remittance of £10.}

    \textit{bank remittance voucher} (=an official statement or receipt that is given to someone to prove that their accounts are correct or that money has been paid)
\end{DefWord}


\begin{DefWord}{reproduce,reproduction}[reproduce]
    if an animal or plant reproduces, or reproduces itself, it produces young plants or animals
    \textit{The turtles return to the coast to reproduce.}

    to make a photograph or printed copy of something
    \textit{Klimt's artwork is reproduced in this exquisite book.}

    to make something happen in the same way as it happened before (repeat, copy)
    \textit{British scientists have so far been unable to reproduce these results.}

    to make something that is just like something else
    \textit{With a good set of speakers, you can reproduce the orchestra's sound in your own home.}
\end{DefWord}

\begin{DefWord}{reduce, reduction}[reduce]
    \textbf{reduce somebody/something to something}

    \textbf{reduce somebody to tears/silence etc} to make someone cry, be silent etc
    \textit{She was reduced to tears in front of her students.}

    \textbf{reduce somebody to doing something} to make someone do something they would rather not do, especially when it involves behaving or living in a way that is not as good as before
    \textit{Eventually Charlotte was reduced to begging on the streets.}

    \textbf{reduce something to ashes/rubble/ruins}
    to destroy something, especially a building, completely
    \textit{A massive earthquake reduced the city to rubble. 一场大地震把这座城市夷为废墟。 }

    to change something into a shorter simpler form
    \textit{Many jobs can be reduced to a few simple points.}
\end{DefWord}