\section{S, s}

\begin{DefWord}{succession}
    A succession of military defeats weakened the aggressor.
\end{DefWord}

\begin{DefWord}{successor}
    \textit{I'm sure she will be a worthy successor.}
\end{DefWord}

\begin{DefWord}{surprise}
\end{DefWord}

\begin{DefWord}{section}
    one of the parts that something such as an object or place is divided into
    \textit{the residential section (住宅区)}
    \textit{the business section (商业区)}
    \textit{a section of lines}
    \textit{all sections of whole land (在全国各地)}

    one of the separate parts of a structure, piece of furniture etc that you fit together to form the whole
    \textit{The boats were built in Scotland, and transported to Egypt \textbf{in sections.}}

    a separate part of a book, newspaper, document, report etc

    a separate group within a larger group of people
    \textit{a large section of the American public}

    one of the parts of a law or a legal document
    \textit{Article I, Section 8 of the US Constitution}

    a picture that shows what a building, part of the body etc would look like if it were cut from top to bottom or side to side 剖面图
    \textit{Here's the outside view, and here are the floors in section.}

    to officially force someone with a mental illness to go to a psychiatric hospital, because they are dangerous to themselves or other people

    to separate something into parts
    \textit{Peel and section the oranges.}

    to cut a very thin flat piece from skin, a plant etc so that you can look at it under a microscope
\end{DefWord}

\begin{DefWord}{segment, segmentation, segmental}[segment]
    a part of something that is different from or affected differently from the whole in some way

    to divide something into parts that are different from each other

    segmentation: when something divides or is divided into smaller parts
    \textit{the segmentation of society}

    segmental: of, relating to, or having the form of a segment and especially the sector of a circle
    \textit{segmental fanlight}

    relating to the individual sounds that make up speech, as opposed to prosodic features such as stress and intonation
\end{DefWord}

\begin{DefWord}{sequence, sequential}[sequence]
    of, relating to, or arranged in a sequence; SERIAL
\end{DefWord}

\begin{DefWord}{subsequent, subsequence, subsequently}[subsequent]
    coming after something in time; following.
\end{DefWord}

\begin{DefWord}{sequel}
    a published, broadcast, or recorded work that continues the story or develops the theme of an earlier one.
\end{DefWord}

\begin{DefWord}{subtract}
    subtract sth from sth
\end{DefWord}

\begin{DefWord}{suspect, suspicion}
\end{DefWord}

\begin{DefWord}{susceptible}
\end{DefWord}

\begin{DefWord}{suspend, suspension}
\end{DefWord}

\begin{DefWord}{sustain, sustainable, sustainability}[sustain]
    维持
    e.g. \textit{The salary couldn't sustain her shopping spree.}
    
    支撑
    e.g. \textit{It's a wonder that the tree can sustain the weight of such heavy snow.}
    
\end{DefWord}

\begin{DefWord}{suicide, suicidal}[suicide]
    \textbf{commit suicide}

    \textit{My mother \textbf{attempted suicide} on many occasions.}

    \textit{He apparently left a \textbf{suicide note} on his desk} (=letter explaining his reasons for killing himself).

    \textbf{something drives him to suicide}

    \textbf{suicide attack/bombing}

    suicidal: 
    wanting to kill yourself
    \textit{She was depressed and almost suicidal.}

    \textit{For many years before treatment, Clare had \textbf{suicidal tendencies.}}

    likely to lead to death:
    \textit{It was suicidal trying to put out that fire.试图去扑灭那火就是在找死. }

    likely to lead to a lot of damage or trouble: 
    \textit{Her economic policies would prove suicidal for our economy.}
\end{DefWord}

\begin{DefWord}{subconscious, subconsciously}
    subconscious feelings, desires etc are hidden in your mind and affect your behaviour, but you do not know that you have them
    \textit{a subconscious fear of failure}

    —subconsciously adverb:
    \textit{Subconsciously, he blames himself for the accident.}
\end{DefWord}

\begin{DefWord}{subvert, subversion}[subvert]
    to try to destroy the power and influence of a government or the established system
    \textit{an attempt to subvert the democratic process}

    to destroy someone's beliefs or loyalty
\end{DefWord}

\begin{DefWord}{spectator}
    someone who is watching an event or game


\end{DefWord}

\begin{DefWord}{spectacle}
    a very impressive show or scene

    an unusual or interesting thing or situation that you see or notice – used especially in order to show disapproval不同寻常的事[现象]〔尤含贬义〕:

    眼镜
\end{DefWord}

\begin{DefWord}{spectacular}
\end{DefWord}

\begin{DefWord}{survive, survival}[survive]
\end{DefWord}

\begin{DefWord}{subjective}
\end{DefWord}

\begin{DefWord}{submit}
    to give a plan, piece of writing etc to someone in authority for them to consider or approve
    \textit{All applications must be submitted by Monday.}

    to agree to obey someone or something or to go through a process, especially when you have no choice〔尤指无可选择时〕同意服从[遵守，接受]，顺从 (SYN  give in)
    \textit{Derek has agreed to submit to questioning.}

    formal law to suggest or say something建议，主张
    \textbf{submit (that)}
    \textit{I submit that the jury has been influenced by the publicity in this case.}
\end{DefWord}

\begin{DefWord}{seduce}
    to persuade someone to have sex with you, especially in a way that is attractive and not too direct
    \textit{The professor was sacked for seducing female students. 这个教授因诱奸女学生而被解雇. }
    \textit{Are you trying to seduce me? 你是在勾引我吗？}

    to make someone want to do something by making it seem very attractive or interesting to them
    \textit{I was young and seduced by New York. 我当时年轻，抵挡不住纽约的诱惑. }

    \textbf{seduce somebody into doing something}
    \textit{Leaders are people who can seduce other people into sharing their dream. 领导人就是要能够说服别人来共同实现他们的梦想. }

    \begin{remark}
        \textbf{Seduce} is often passive in this meaning.
    \end{remark}
\end{DefWord}