\section{T, t}

\begin{DefWord}{transcipt}
    written copy of a speech
\end{DefWord}

\begin{DefWord}{transribe}
\end{DefWord}

\begin{DefWord}{transfer}
\end{DefWord}

\begin{DefWord}{transform}
\end{DefWord}

\begin{DefWord}{transformer}
\end{DefWord}

\begin{DefWord}{transit, transition}[transit]
\end{DefWord}

\begin{DefWord}{transmit, transmission}[transmit]
\end{DefWord}

\begin{DefWord}{tranplant}
\end{DefWord}

\begin{DefWord}{transport, transportation}[transport]
\end{DefWord}

\begin{DefWord}{trespass}
    to go onto someone's private land without their permission
    \textit{She was arrested for trespassing on government property.}

    trespass on something (to unfairly use more than you should of someone else's time, help etc for your own advantage)
    \textit{It would be trespassing on their hospitality to accept any more from them.}
    \textit{May I trespass on your patience once more.}
\end{DefWord}

\begin{DefWord}{tractor}
\end{DefWord}

\begin{DefWord}{traction}
\end{DefWord}

\begin{DefWord}{terrible}
\end{DefWord}

\begin{DefWord}{terrify}
\end{DefWord}

\begin{DefWord}{terrific}
    （informal) very good, especially in a way that makes you feel happy and excited
    \textit{That's a terrific idea!}

    very large in size or degree
    \textit{He drank a terrific amount of beer.}
\end{DefWord}

\begin{DefWord}{terror}
    a feeling of extreme fear
    \textit{People \textbf{fled in terror} as fire tore through the building.}

    an event or situation that makes people feel extremely frightened, especially because they think they may die
    t 
    \textit{he terrors of war}

    violent action for political purposes 恐怖活动
    \textit{The resistance movement started a campaign of terror.}

    (informal) a child who is difficult to control
    \textit{That Johnson kid's a real little terror!}

\end{DefWord}

\begin{DefWord}{terroist}
\end{DefWord}

\begin{DefWord}{terrorism}
\end{DefWord}

\begin{DefWord}{transmit, transmission, transmitter}[transmit]
\end{DefWord}

\begin{DefWord}{typography}
\end{DefWord}