\section{V, v}

\begin{DefWord}{visual, visualize}[visual]
\end{DefWord}

\begin{DefWord}{visible, visibility, invisible}[visible]
\end{DefWord}

\begin{DefWord}{VOLVE}
\end{DefWord}

\begin{DefWord}{vocal, vocalize, vocally, vocalization, vocalist}[vocal]
    expressing strong opinions publicly, especially about things that you disagree with (outspoken)
    \textit{Foley has been particularly vocal in his criticism of the government.}

    relating to the voice or to singing
    \textit{Allison's vocal style is influenced by country and blues music.艾莉森的演唱风格受到乡村音乐和布鲁斯音乐的影响. }

    vocalize: to make a sound or sounds with your voice
\end{DefWord}

\begin{DefWord}{vocation}
    the feeling that the purpose of your life is to do a particular type of work, especially because it allows you to help other people

    \textit{Jan has a \textbf{vocation for} teaching.简对教书有一种使命感. }

    a particular type of work that you feel is right for you

    \textit{At 17 she \textbf{found} her \textbf{true vocation} as a writer. 17岁时她找到了自己真正的使命——当一名作家. }
\end{DefWord}

\begin{DefWord}{vie}
    C'est la vie. (This is life.)
\end{DefWord}

\begin{DefWord}{vitamin}
\end{DefWord}

\begin{DefWord}{vital, vitality}[vital]
    extremely important and necessary for something to succeed or exist 极其重要的，必不可少的 (SYN  crucial)
    \textit{The samples could give scientists vital information about long-term changes in the Earth's atmosphere.}

    \textit{It is vital that you keep accurate records.}

    full of energy in a way that is exciting and attractive
    \textit{Rodgers and Hart's music sounds as fresh and vital as the day it was written.}

    vitality:/vaɪˈtæləti/
    great energy and eagerness to do things
    \textit{Despite her eighty years, Elsie was full of vitality.}

    the strength and ability of an organization, country etc to continue
    \textit{The process of restructuring has injected some much-needed vitality into the company.}
\end{DefWord}

\begin{DefWord}{vivid}
\end{DefWord}

\begin{DefWord}{vivacious}
    /vəˈveɪʃəs/

    someone, especially a woman, who is vivacious has a lot of energy and a happy attractive manner : used to show approval (syn lively)
    \textit{a vivacious personality}
\end{DefWord}

\begin{DefWord}{vigor, vigorous}[vigor]
    physical or mental energy and determination 活力，精力；热情
    \textbf{with vigour}
    \textit{He began working with renewed vigour.}

    vigorous: using a lot of energy and strength or determination
    \textit{Your dog needs at least 20 minutes of \textbf{vigorous exercise} every day.}
    \textit{Environmentalists have begun a vigorous campaign to oppose nuclear dumping in the area.}

    strong and healthy 强健的，精力旺盛的:
    \textit{a vigorous young man}
\end{DefWord}

\begin{DefWord}{vigilance, vigilant}[vigilant]
    giving careful attention to what is happening, so that you will notice any danger or illegal activity
    \textit{Please \textbf{remain vigilant} at all times and report anything suspicious.}
\end{DefWord}
